---
output: html_document
params:
    url: "https://www.sportchek.ca/categories/electronics/headphones-speakers/headphones/earbuds-in-ear/true-wireless/product/jaybird-vista-2-true-wireless-sport-headphones-color-333364786_01-333364786.html"
    sitename: "PriceBeaver"
---
    
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Source the products script for later use
source('products.R')
# Source the saving script for later use
source('dbsave.R')
library("urltools", "ggplot2", "plotly")
product <- product_collection$find(paste0('{"url" : "',params$url,'"}'))

page_title <- paste(
  params$sitename,
  "-",
  product$product_name,
  "from",
  urltools::suffix_extract(product$domain)$domain
)
```


---
title: `r page_title`
---

## `r product$product_name`

This product was last scraped on `r as.Date(product$last_scraped)` with a price of \$`r product$last_price`

### Price History

```{r echo=FALSE}
price_data <- price_collection$find(paste0('{"request_url" : "',params$url,'"}'), '{"_id" : 0, "price": 1, "date_scraped" : 1}')

price_plot <- ggplot(
  price_data,
  aes(x = date_scraped, y = price)
) + geom_line()
plotly::ggplotly(price_plot)
```

```{r echo=FALSE, results='asis'}
product_prices <- tibble(
  "Highest Price" = product$highest_price,
  "Lowest Price" = product$lowest_price,
  "Typical Price" = product$typical_price
)
library(knitr)
kable(product_prices,
      caption = "Price Information")
